---
title: "Cross Section Spatial Autocorrelation Model (SAC) with Generalized Spatial Two Stage Least Squares (GSTSLS) estimator report"
author: "`r format(Sys.time())`"
output: pdf_document
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}
    \includegraphics[width=2in,height=2in]{tobleR.png}\LARGE\\}
  - \posttitle{\end{center}}
params:
  general_observations: NA
  data_file: NA
  data_type: NA
  original_data: NA
  spatial_weights_matrix: NA
  model_specification: NA
  model_endog: NA
  model_instruments: NA
  model_options: NA
  model_summary: NA
  model_impacts: NA
---

```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
```

```{r echo=FALSE, results='asis'}
cat(params$general_observations)
```

# Data

* File name: `r params$data_file`
* Data type: `r params$data_type`
* Dimensions: `r dim(params$original_data)[1]` rows and `r dim(params$original_data)[2]` columns.

# Spatial weights matrix

`r params$spatial_weights_matrix`

# Model

## Model specification

```{r echo=FALSE, results='asis'}
cat(params$model_specification)
```

* Endogenous variables: `r params$model_endog`
* External instruments variables: `r params$model_instruments`

## Model options

* Heteroskedasticity correction: `r if("is_robust" %in% params$model_options) "Yes" else "No"`
* Use secondary spatial weights matrix: `r if("use_secondary_w_matrix" %in% params$model_options) "Yes" else "No"`


## Model summary

```{r echo=FALSE}
params$model_summary
```

## Model impacts

```{r echo=FALSE}
params$model_impacts
```
